Survival Compass: Statistical Insights into Lung Cancer Patients' Journey Post-Diagnosis

### 2024-03-30 paper/paper.qmd
Used ChatGPT to create interesting hook in the introduction and to come up with a creative and unique title. Thus updated llm/usage

---
title: "From Theory to Practice: Investigating Treatment Responses in Breast Cancer"
subtitle: "My subtitle if needed"
author: 
  - First author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Survival Compass: Statistical Insights into Lung Cancer Patients' Journey Post-Diagnosis"
subtitle: "My subtitle if needed"
author: 
  - First author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
